---
title: "Lab 7 multiple linear regression"
author: "Hollie Pennington"
date: "11/8/2021"
output: html_document
---

```{r setup, include=TRUE, warning = FALSE, message = FALSE }
knitr::opts_chunk$set(echo = TRUE, echo = TRUE, message = FALSE, warning = FALSE)
#attach packages 

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

##intro to ggpairs

Use GGally::gpairs()function to create a pairs plot. 

```{r}
ggpairs(penguins)
```

```{r}
#create a subset of data
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))

ggplot(data = penguins, aes(x = bill_depth_mm, y=body_mass_g, group = species))+ 
  geom_point(aes(color = species)) + 
  geom_smooth(method = "lm")
```

## Multiple linear regression - penguins 

Use multiple linear regression to try to understand the relationship between multiple predictor variables and a single continuous outcome variable (body mass). 

```{r}
penguins_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

#Return just the coefficients 
penguins_lm
```

How would you interpret this coefficient for flipper_length_mm? 
On average we would expect, on average, a 1 mm increase in flipper length to be associated with a 51.54 grams increase in body mass. 
OR 
We would expect, on average, a 51.54 g increase in penguin body mass for each 1 mm increase in flipper length, if everything else is constant 
The y-int here is useless 

```{r}
summary(penguins_lm)
```
If we are doing multiple linear regression than we are looking for the adjusted r-squared, 

What does the r-squared value mean? 

70% of the vairance in our penguin body mass, can be explained by this model 
A square just is what it is. It is neither good nor bad

###Use 'broom' functions tidy and glance 

Use broom::tidy to get the coefficeint summary in data frame 
use broom::glance to get the model summary in data frame 

```{r}
penguin_lm_tidy <- tidy(penguins_lm)
penguin_lm_tidy
```
Try use in-line code to refer to (print) the bill depth coefficient 

'r penguin_lm_tidy$estimate[3]'.

```{r}
penguin_lm_glance <- glance(penguins_lm)

penguin_lm_glance
```
#try another model 

We have thought really hard, done a literature review, consulted with experets, deeply explored our data and decided that the three most critical variables to inlcude in this model (with body mass as the outcome variable) are: 
-flipper length 
-species 
-sex 

Task: create a multiple linear regression model using those 3 predictor variables 

The take a look at the model outputs and interpret the coefficients with a neighbor. 


```{r}
penguin_lm2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)
penguin_lm2
```

Our reference level for sex is female because the input that shows up is male. 

mass(g) = - 365.82 + 20.02 (flip(mm)) - 87.63(chinstraps) + 836.3(gentoo) + 530.38(male)


Interpret: 
speciesGentoo: If everything is the same, then on average, we expect a  gentoo penguin to weight 836.3 more than an a adelie penguin. 
chinstraps: If everything else is the same, then on average, we expect a chinstrap penguin to weigh 87.63 less than adelie penguins. 
Male: if everything else is the same, then on average, we expect a male penguin to weigh 530.38 grams more than a female penguin. 

If I am trying to predict the mass on a penguin with a flipper length 180 mm, female chinstrap penguin
mass(g) = -365.82 + 180 mm + 1(chinstrap) + 0(gentoo) + 0(male)


### use broom::augment() to see predicted values 

```{r}
augment(penguin_lm2)
```
```{r}
plot(penguin_lm2) 
#check residuals 
```

If we look at qq plot we can see if the residuals are normal distrubited. Here they do appear to be normally distributed. 

Scale location: does there appear to be vertical constant spread in residual distribution, if this is true, then it should look like good random spread. 

- conceptual understanding and expertise allows me to responsily determine that penguin species, sex and flipper length are reasonable predictor variable (make sure you're thinking hard about variables and different variable combinations)
- diagnostic plots all check out for normality of residuals, homoscedasticity, and no worrisome outlieres (<< last one is not an assumption)

## Make output tables 

using modelsummary:

```{r}
modelsummary(penguin_lm2)
```
```{r, results = "asis"}
stargazer(penguin_lm2, type = "html")
```

